%! TEX root=../main.tex

\section{Responses}
  \subsection{Response 1}
    \begin{quotation}
      Listening is something that comes easier to me than talking.
        As I indicated by my goals, one of which is to be less concise, I do not
        often just volunteer information about myself.  I prefer to listen to
        what others have been thinking about or learn more about them. I can
        relate to Erin because I would probably be wondering why I did not get
        the bonus that they had talked about, although instead of making a fuss
        about it I would probably have just checked out of the situation.
        Overall, the way Ed started the conversation, despite the fact he was
        trying to surprise her, would have caused anyone to be a bit upset.
        I do not really think that gender had anything to do with this situation
        and the reactions they had. It seems to me that this would have been
        more influenced by personality, not gender.

      I believe that we can define listening as processing information or
        emotions from others.  One article I read when studying effective and
        not effective listening skills, which talks about things effective
        listeners do states, “These behaviors include responses such as
        ``uh huh'' and ``hmmm,'' as well as other nonverbal behaviors including
        nodding, smiling, and adjusting one's posture. Other active listening
        behaviors include asking questions, making eye contact, and not
        interrupting the speaker” (Fedesco, 2015).  Asking questions can help
        you to not only better remember information, but also better understand
        it. That article goes on to say that the more you use those behaviors
        indicates how invested you are in a certain conversation. Another
        article I read makes this claim that being a good listening can offer,
        ``A greater number of friends and social networks, improved self-esteem
        and confidence, higher grades at school and in academic work, and even
        better health and general well-being'' (Listening Skills). This means
        that being a good listener can provide a large number of benefits. Being
        a good or bad listener would definitely affect your grades in school.

      As I tried to find a difference between male and female in terms of
        listening, I did not find anything that indicated one listens better
        than the other.  I read an article which states, “Despite activating
        different activity centers within the brain, genders perform equally on
        measures of cognitive function. This means that although we listen and
        assimilate information differently, the difference does not appear to
        affect cognition or our ability to listen” (McCormick,2018). Therefore,
        our brains may function in a different way, but that does not indicate
        that either men or women listen better simply based on their gender.
        I would say my research aligns pretty well with how I communicate, with
        exception to the occasionally accidental interruption.  Therefore, I
        would still classify myself as a good listener.  I often ask questions,
        make eye contact, and am sympathetic to the person speaking.

      Effective Listeners Top 5 List:
      \begin{enumerate}
        \item Asking questions
        \item Making eye contact
        \item Not interrupting
        \item Smiling
        \item Being polite
      \end{enumerate}

      Ineffective Listeners Top 5 List
      \begin{enumerate}
        \item Interrupting
        \item Looking away
        \item Crossing their arms
        \item Not reacting with smiles or frowns (not sympathetic)
        \item Often changing the subject
      \end{enumerate}
    \end{quotation}

    \paragraph{This is a response to Thora Smith on Post ID 43465667}
      I completely agree with you on the side of how most \textit{anyone} would
        be upset if being approached the same way Erin was prior to the
        ``surprise/joke'' about her bonus amount was realized. If my boss were
        to have come to me in a similar manner, I am sure I would have reacted
        in the exact same way as Erin did when she felt she was being valued
        by her company less than she was worth.

      I also believe, like you do, that \textit{asking questions} is an
        important part of being an effective listener in \textbf{any} scenario.
        I do have on question about this though (or rather, more a solicitation
        for advice) which maybe you can help me with. When a question regarding
        what someone is telling you comes into your head, do you ask it right
        away (thereby interupting the speaker's conversational flow) or do you
        hold the question until after they are done speaking, when it may
        \textit{no longer be relevant}? This is something I always have
        difficulty with. Sometimes my question is answered by the speaker by
        listening to the rest of the story, but sometimes it is not and when
        I bring it up again at the end of a conversation sometimes the other
        party does not even remember that far back into the conversation to
        answer! Incredibly frustrating on occassion, depending on the situation
        this occurs. What is your opinion on that matter?
